BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-08-09 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
revamp paragraph on data themes

Thematically, many of the variables which BarnebyLives collects information on are tailored to Western North America. 
However, the package supports the use of a 'domain' being drawn over any of the conterminous United States. 
Several of the attributes which it collects and displays on labels, relate to topics in which more senior curators are interested, i.e. the administrative information on Township Section and Range (or 'TRS'), but are considered less valuable in other geographic regions.  
Further several of the abiotic variables on which it acquires information on: slope, aspect, and geology, have long been considered prominent drivers of plant distributions in semi-arid and montane environments and are warranted on an herbarium label for specimens collected from these environments, whereas curators in other regions may find this information superfluous. 
Finally, it is plausible botanists in other geographic areas are less interested in displaying which land management agency has jurisdiction over a collection; however in the Western United States we believe this is useful information which may help a collector interested in revisiting a site to determine if they will require permits for access or to make new collections.

>>>>

BarnebyLives allows for the usage of 'domains' (i.e., custom geographic extents), which analysis is restricted to, allowing users to specify any portion of the United States for setting up their instance. 
However, many of the environmental and geographic variables that BarnebyLives collects information on are tailored to Western North America. 
Several of the variables that BarnebyLives collects and displays on labels relate to topics in which more senior Western curators are interested, that is, the administrative information on Township Section and Range (or 'TRS') or the agency administering public land, but are considered less valuable–or even unavailable or inapplicable–in other geographic regions.
Environmental variables such as slope, aspect, and geology are prominent drivers of plant distributions in semi-arid environments and warrant inclusion on herbarium labels for specimens from Western environments, but curators may consider them superfluous for other environments. 
Accordingly, users may consider developing new functionality that either removes or supplements the default variables to better reflect regional needs.
